Realizing temporal graphs from fastest travel times

### 2023-02-01 ICALP23-RealizingTemporalGraphs.tex
Small changes 1st Feb

$\{x^T,y^T\},\{x^T,y^F\}, \{x^F,y^T\},\{x^F,y^F\}$.
\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x$ appear in $c$. If $X$ appears non-negated in $c$ we add edge $\{c,x^T\}$. If $x$ appears negated in $c$ we add edge $\{c, x^F\}$.
\end{itemize}
This finishes the construction of $G$.

@@

	\draw [dotted] (x3f) [out=30,in=150] to (x4t);
	\draw [dotted] (x3f) [out=30,in=150] to (x4f);
\end{tikzpicture}
}
\caption{Example of the temporal graph $(G_\phi,\lambda)$ from the NP-hardness reduction, 
	where the 3-SAT formula $\phi$ is of form $\phi = (x_1 \vee \overline{x_2} \vee x_3) \wedge (\overline{x_1} \vee x_2 \vee x_4)$.
For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neg j$) with a dotted line.
Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
where all unlabeled edges get the label $2$.}
\end{figure}
\end{proof}

@@

    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
    We repeat this for all vertices of interest, and all segments,
    which produces $O(k^{k^2})$ new guesses.
    %
    For an example see~\cref{fig:FPT-guessG7}.
    % counter for guesses continues
    \setcounter{guesscounter}{\value{enumi}}
\end{enumerate}
%
\begin{figure}[ht]
    \centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			%%%S_uv
			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
			\draw (v1) -- (v2) -- (vp1) -- (vp);

>>>>

$\{x^T,y^T\},\{x^T,y^F\}, \{x^F,y^T\},\{x^F,y^F\}$.
\item For each clause $c$ in $\phi$ we add one edge for each literal. Let $x$ appear in $c$. If $X$ appears non-negated in $c$ we add edge $\{c,x^T\}$. If $x$ appears negated in $c$ we add edge $\{c, x^F\}$.
\end{itemize}
This finishes the construction of $G$.
For an example see~\cref{fig:NP-example}.

@@

	\draw [dotted] (x3f) [out=30,in=150] to (x4t);
	\draw [dotted] (x3f) [out=30,in=150] to (x4f);
\end{tikzpicture}
}
\caption{Example of the temporal graph $(G_\phi,\lambda)$ from the NP-hardness reduction, 
	where the 3-SAT formula $\phi$ is of form $\phi = (x_1 \vee \overline{x_2} \vee x_3) \wedge (\overline{x_1} \vee x_2 \vee x_4)$.
For the simplicity we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neg j$) with a dotted line.
Presented is the labeling of $G_\phi$, corresponding to the assignment $x_1=x_2=\textsc{True}$ and $x_3,x_4=\textsc{False}$,
where all unlabeled edges get the label $2$.
\label{fig:NP-example}}
\end{figure}
\end{proof}

@@

    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
    We repeat this for all vertices of interest, and all segments,
    which produces $O(k^{k^2})$ new guesses.
    %
    For an example see~\cref{fig:FPT-guessG7}.
    % counter for guesses continues
    \setcounter{guesscounter}{\value{enumi}}
\end{enumerate}
%
\begin{figure}[h]
    \centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			%%%S_uv
			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
			\draw (v1) -- (v2) -- (vp1) -- (vp);
